A planetary collision afterglow and transit of the resultant debris cloud

### 2023-10-12 src/tex/ms.tex
[showyourwork] overleaf sync

\usepackage{glossaries}
\glsdisablehyper    % no hyperlink because we're not printing the glossary
%% ACRONYMS %%
\newacronym{asassn}{ASAS-SN}{All Sky Automated Survey for Supernovae}
\newacronym{asas}{ASAS}{All Sky Automated Survey}
\newacronym{neowise}{NEOWISE}{Near-Earth Object Wide-field Infrared Survey Explorer}
\newacronym{lcogt}{LCOGT}{Las Cumbres Observatory Global Telescope}
\newacronym{atlas}{ATLAS}{Asteroid Terrestrial-impact Last Alert System}
\newacronym{aavso}{AAVSO}{American Association of Variable Star Observers}
\newacronym{banzai}{BANZAI}{Beautiful Algorithms to Normalize Zillions of Astronomical Images}
\newacronym{road}{ROAD}{Remote Observatory Atacama Desert}
\newacronym{ccd}{CCD}{charge-coupled device}
\newacronym{wise}{WISE}{Wide-field Infrared Survey Explorer}
\newacronym{sed}{SED}{spectral energy distribution}
\newacronym{tess}{TESS}{Transiting Exoplanet Survey Satellite}
\newacronym{alma}{ALMA}{Atacama Large Millimeter Array}
\newacronym{mast}{MAST}{Mikulski Archive for Space Telescopes}

>>>>

%\usepackage{glossaries}
%\glsdisablehyper    % no hyperlink because we're not printing the glossary
%%% ACRONYMS %%
%\newacronym{asassn}{ASAS-SN}{All Sky Automated Survey for Supernovae}
%\newacronym{asas}{ASAS}{All Sky Automated Survey}
%\newacronym{neowise}{NEOWISE}{Near-Earth Object Wide-field Infrared Survey Explorer}
%\newacronym{lcogt}{LCOGT}{Las Cumbres Observatory Global Telescope}
%\newacronym{atlas}{ATLAS}{Asteroid Terrestrial-impact Last Alert System}
%\newacronym{aavso}{AAVSO}{American Association of Variable Star Observers}
%\newacronym{banzai}{BANZAI}{Beautiful Algorithms to Normalize Zillions of Astronomical Images}
%\newacronym{road}{ROAD}{Remote Observatory Atacama Desert}
%\newacronym{ccd}{CCD}{charge-coupled device}
%\newacronym{wise}{WISE}{Wide-field Infrared Survey Explorer}
%\newacronym{sed}{SED}{spectral energy distribution}
%\newacronym{tess}{TESS}{Transiting Exoplanet Survey Satellite}
%\newacronym{alma}{ALMA}{Atacama Large Millimeter Array}
%\newacronym{mast}{MAST}{Mikulski Archive for Space Telescopes}
